Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-05-21 msc-publication.tex
Remove Klemp2011 figure.

The test was integrated forward by 5 hours on the BTF, SLEVE and cut cell grids, and a regular grid with flat terrain.  Maximum vertical velocities are compared with the results from \citet{klemp2011} in figure~\ref{fig:resting} (note different vertical scales).  In agreement with \citet{klemp2011}, vertical velocities are larger on more distorted grids.  However, magnitudes are smaller comparing results on the terrain following grids with those from \citet{klemp2011}.  Using the model from \citet{weller-shahrokhi2014}, which includes a curl-free pressure gradient formulation, $w$ reaches a maximum of \(\sim \SI{0.35}{\meter\per\second}\) on the BTF grid, compared with a maximum of \(\sim \SI{7}{\meter\per\second}\) found by \citet{klemp2011} using their improved horizontal pressure gradient formulation.

@@

\begin{figure*}
	\centering
	\includegraphics{../msc-publication-fig-resting/fig-resting.pdf}
%
	\caption{Maximum spurious vertical velocity, \(w\) (\si{\meter\per\second}), in the resting atmosphere test with results on (a) BTF, SLEVE, Hybrid Terrain Following (HTF) and Smoothed Terrain Following (STF) coordinates from \citet{klemp2011} using their improved horizontal pressure gradient formulation, (b) BTF, SLEVE, cut cell and regular grids using the model from \citet{weller-shahrokhi2014} which includes a curl-free pressure gradient formulation.  Note that vertical scales differ.}
	\label{fig:resting}
\end{figure*}

>>>>

The test was integrated forward by 5 hours on the BTF, SLEVE and cut cell grids, and a regular grid with flat terrain.  Maximum vertical velocities are presented in figure~\ref{fig:resting}.  In agreement with \citet{klemp2011}, vertical velocities are larger on more distorted grids.  However, magnitudes are smaller comparing results on the terrain following grids with those from \citet{klemp2011}.  Using the model from \citet{weller-shahrokhi2014}, which includes a curl-free pressure gradient formulation, $w$ reaches a maximum of \(\sim \SI{0.35}{\meter\per\second}\) on the BTF grid, compared with a maximum of \(\sim \SI{7}{\meter\per\second}\) found by \citet{klemp2011} using their improved horizontal pressure gradient formulation.

@@

\begin{figure}
	\centering
	\includegraphics{../msc-publication-fig-resting/fig-resting.pdf}
%
	\caption{Maximum spurious vertical velocity, \(w\) (\si{\meter\per\second}), in the resting atmosphere test with results on BTF, SLEVE, cut cell and regular grids using the model from \citet{weller-shahrokhi2014} which includes a curl-free pressure gradient formulation.}
	\label{fig:resting}
\end{figure}
